|

### 2024-08-11 doc/paper.qmd
EM4 calc. update: at lest 5 obs. small profits

During the preparation step, 8,265 firms and 20,521 firm-year observations (all due to the second filtration step) were dropped, resulting in a final dataset with 18,040 non-financial firms and 123,469 firm-year observations. The differences in the numbers between the prepared dataset and the figures mentioned in the paper (70,955 firm-year observations and 8,616 non-financial firms) could be due to assumptions outlined in @sec-research_design_assumptions, such as variations in initial datasets, data updates, and filtering criteria. However, the original paper might have included additional data cleaning steps not explicitly mentioned, such as handling outliers, specific industry exclusions, or other criteria, which could affect the final counts.
## table 2 correctly referenced?
Given that the number of observations in this project is significantly higher than in the original study, Table 1 from @Leuz_2003 was partially replicated (focusing only on columns related to countries and firm-year observations) to highlight specific discrepancies that could arise for certain countries. The results in the Table 2 below show a higher number of firm-year observations for almost all countries compared to the paper by @Leuz_2003, likely due to database updates leading to a more comprehensive dataset. The trend in the number of firm-year observations across countries is consistent with the original study, with larger capital markets like Japan, the United Kingdom, and the United States having the highest numbers. The distribution of observations in my dataset shows higher mean and median values compared to the paper by @Leuz_2003, indicating a greater overall number of firm-year observations, while the minimum values are relatively close, suggesting that the overall distribution of observations across countries remains broadly similar.

>>>>

During the preparation step, 8,265 firms and 20,521 firm-year observations (all due to the second filtration step) were dropped, resulting in a final dataset with 18,040 non-financial firms and 123,469 firm-year observations. The differences in the numbers between the prepared dataset and the figures mentioned in the paper (70,955 firm-year observations and 8,616 non-financial firms) could be due to assumptions outlined in @sec-research_design_assumptions, such as variations in initial datasets, data updates, and filtering criteria. However, the original paper might have included additional data cleaning steps not explicitly mentioned, such as handling outliers, specific industry exclusions, or other criteria, which could affect the final counts.

Given that the number of observations in this project is significantly higher than in the original study, Table 1 from @Leuz_2003 was partially replicated (focusing only on columns related to countries and firm-year observations) to highlight specific discrepancies that could arise for certain countries. So, the results in the Table 2 below show a higher number of firm-year observations for almost all countries compared to the paper by @Leuz_2003, likely due to database updates leading to a more comprehensive dataset. The trend in the number of firm-year observations across countries is consistent with the original study, with larger capital markets like Japan, the United Kingdom, and the United States having the highest numbers. The distribution of observations in my dataset shows higher mean and median values compared to the paper by @Leuz_2003, indicating a greater overall number of firm-year observations, while the minimum values are relatively close, suggesting that the overall distribution of observations across countries remains broadly similar.
